### 2009-01-27 articles/2009/geoinformatics/article.tex
more text and figures
git-svn-id: https://svn.osgeo.org/qgis/trunk@10032 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@

QGIS offers a growing number of common GIS functionality provided by core
features and plugins. They are presented in a friendly graphical user
interface, clearly seperated into a menu bar, tool bars, status bar, map view,
overview, and map legend (see Figure~\ref{fig:qgis10}).

\begin{figure}[h]
   \begin{center}
   \caption{Quantum GIS 1.0.0 'Kore'}\label{fig:qgis10}\smallskip
   \includegraphics[clip=true, width=\textwidth]{qgis10}
\end{center}
\end{figure}

The menu and tool bars give access to all QGIS features and at a glance
provide following features:

@@

@@

\textbf{External Plugins} are all written in Python. They are stored in
an official, external repository and maintained by the individual author. The
user can easily add those Plugins to QGIS with the Python Plugin Installer
(See Figure~\ref{fig:python-plugin}).

\begin{figure}[h]
   \begin{center}
   \caption{QGIS Python Plugin Installer}\label{fig:python-plugin}\smallskip
   \includegraphics[clip=true, width=\textwidth]{python-plugin-installer}
\end{center}
\end{figure}

>>>>

\subsection{Graphical User Interface}

Working with QGIS is simple and intuitive as you are presented with a
modern and friendly graphical user interface (GUI) based on QT4. All
functionalities are clearly seperated (see Figure~\ref{fig:qgis10}).

\begin{figure}[h]
   \begin{center}
   \caption{Quantum GIS 1.0.0 'Kore'}\label{fig:qgis10}\smallskip
   \includegraphics[clip=true, width=12cm]{qgis10}
\end{center}
\end{figure}

A \textbf{menu bar} provides access to QGIS features using a standard
hierarchical menu, with icons of the corresponding tools as they appear on
the tool bar and with keyboard shortcuts. The \textbf{tool bar} icons provide
direct access to functions of the menu bar, plus additional tools for
interacting with the map view. To make the GUI appear clearer, tool bar icons
can be switched on and off. The 'business end' of QGIS is the \textbf{map
view}. Various operations can be performed on the map, such as pan, zoom-in,
zoom-out, select or query. It is tightly bound to the \textbf{map legend},
where layer visibility is managed and set to a z-order, meaning layers
listed nearer the top of the legend are drawn over layers listed lower down.
The \textbf{map overview} area provides a full extent view of selected layers
with a rectangle showing the current map extent in the map view. And the
\textbf{status bar} finally shows the current mouse pointer position in map
coordinates, view extents of the map view, the progress of rendering or
analysis activities, the current map scale depending on the defined
Coordinate Reference System (CRS) and information about available external
plugin updates.

@@

QGIS offers a growing number of common GIS functionality provided by core
features and plugins and at a glance provide following features:

@@

\begin{figure}[h]
   \begin{center}
   \caption{QGIS Geoprocessing Tools}
    \label{fig:geoprocessing}\smallskip
   \includegraphics[clip=true, width=8cm]{geoprocessing}
\end{center}
\end{figure}

@@

\textbf{External Plugins} are all written in Python and devided into official
and user contributed plugins. The user can easily add those Plugins to QGIS
with the Python Plugin Installer (See Figure~\ref{fig:python-plugin}).

\begin{itemize}
\item \textbf{Official} external python plugins are stored in an official,
moderated repository at \url{http://pyqgis.org/repo/official} as part of the
official QGIS release and maintained by the individual author.
\item \textbf{User-Contributed} external python plugins are stored in an
unofficial repository at \url{http://pyqgis.org/repo/contributed} and contain
plugins that are not yet mature enough but on the way to the official
repository.
\end{itemize}

Beside these two respositories a few QGIS developers provide and maintain
their own repositories. They can be added to the repository list of the
Python Plugin Installer.

\begin{figure}[h]
   \begin{center}
   \caption{QGIS Python Plugin Installer}\label{fig:python-plugin}\smallskip
   \includegraphics[clip=true, width=14cm]{python-plugin-installer}
\end{center}
\end{figure}
